---
title: "VR2022 Reproduction Script"
author: "Viplav Tuladhar & Alex O. Holcombe"
bibliography: VR2022Report.bib
csl: apa.csl
format: html
editor: visual
---

# Loading of Data/Packages

This file has all the code for the reproduction and further testing for @veríssimo2022 The chunk below loads the packages used and the data as well.

```{r}
#| label: Package, Data and Seed information

library(dplyr); library(ggplot2); library(tidyr); library(lme4); library(psych); library(purrr); library(RColorBrewer); library(patchwork); library(irr); library(corrplot); library(ggsci)

set.seed(1996)

ant <- read.table("Verissimo et al/data/ANT-data.csv", sep = ",", header = TRUE, fileEncoding = "utf-8")
```

## Centering Function Code

The following code chunk reproduces the centering and p-value calculation function used in the VR2022 paper.

```{r}
#| label: centering and p-value function

# Centering
c.  <- function(x) {scale(as.numeric(x), scale=F)}
# p-values
p.lmer <- function(model){
  p.from.t <- function (tval, obs, nf){2*(1-pt(abs(tval), obs-nf))}
  msum <- summary(model)
  mts <- msum$coefficients[, "t value"]
  mdp <- msum$devcomp$dims["N"]
  mfe <- nrow(msum$coefficients)
  mps <- as.matrix(round(p.from.t(mts, mdp, mfe), 4))
  colnames(mps) <- "p value"
  return(mps)
}
```

# Models

## Central Baseline Models (For Log and Raw RTs)

The code for the reproduction of the central baseline model, this is the model that is used by @veríssimo2022 for their linear analysis. This model uses the central cue as the baseline, the double cue is thus removed in the sub-setting phase.

The three measures are calculated as follows, note that Alerting and Orienting use cues for their calculation while Conflict uses flankers $$Alerting = NoCue - Central$$ $$Orienting = Central - Spatial$$ $$Conflict = Incongruent - Congruent$$

```{r}
#| label: Subset data for linear modelling (main model)

#Subset (excluded: participants less than 75% accuracy, incorrect responses, double cue trials)
nrow(ant.main <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Cue!="DOUBLE" & ant$Accuracy==1,]))
length(unique(ant.main$Participant_ID))
#Contrasts (for Sex, Flanker, and Cue)
ant.main$Sex <- factor(ant.main$Sex, levels=c("Female", "Male"))
(contrasts(ant.main$Sex) <- matrix(dimnames=list(levels(ant.main$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.main$Flanker <- factor(ant.main$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.main$Flanker) <- matrix(dimnames=list(levels(ant.main$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.main$Cue <- factor(ant.main$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.main$Cue) <- matrix(dimnames=list(levels(ant.main$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear Main Models and Age Follow-ups (Log and Raw)

# Main Model (Log RT)
m <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main)
print(summary(m), cor=F)
cbind(summary(m)$coefficients, p.lmer(m), confint(m, parm="beta_"))

## Linear analysis (follow-ups)
  
## Baseline: Age=58
m.age.min <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-58) +
                    Flanker * I(Age-58) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.min), cor=F)
cbind(summary(m.age.min)$coefficients, p.lmer(m.age.min))
confint(m.age.min, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=98
m.age.max <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-98) +
                    Flanker * I(Age-98) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.max), cor=F)
cbind(summary(m.age.max)$coefficients, p.lmer(m.age.max))
confint(m.age.max, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=90
m.age.90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-90) +
                   Flanker * I(Age-90) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.90), cor=F)
cbind(summary(m.age.90)$coefficients, p.lmer(m.age.90))
confint(m.age.90, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=74 (smallest alerting effect, in absolute value of the estimate)
m.age.74 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-74) +
                   Flanker * I(Age-74) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.74), cor=F)
cbind(summary(m.age.74)$coefficients, p.lmer(m.age.74))
confint(m.age.74, parm="Cue.ALERTING")

## Under 90
m.age.u90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main[ant.main$Age<90,])
print(summary(m.age.u90), cor=F)
cbind(summary(m.age.u90)$coefficients, p.lmer(m.age.u90), confint(m.age.u90, parm="beta_"))

# Main Model (Raw RT)
  
m.raw <- lmer(RT ~ (1 + Flanker | Participant_ID) +
                    Cue * Flanker +
                    Cue * c.(Age) +
                    Flanker * c.(Age) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.raw), cor = FALSE)
cbind(summary(m.raw)$coefficients, p.lmer(m.raw), confint(m.raw, parm="beta_"))

## Raw analysis (follow-ups)
  
## Baseline: Age=58
m.age.min.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-58) +
                    Flanker * I(Age-58) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.min.raw), cor=F)
cbind(summary(m.age.min.raw)$coefficients, p.lmer(m.age.min.raw))
confint(m.age.min.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=98
m.age.max.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-98) +
                    Flanker * I(Age-98) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.max.raw), cor=F)
cbind(summary(m.age.max.raw)$coefficients, p.lmer(m.age.max.raw))
confint(m.age.max.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=90
m.age.90.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-90) +
                   Flanker * I(Age-90) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.90.raw), cor=F)
cbind(summary(m.age.90.raw)$coefficients, p.lmer(m.age.90.raw))
confint(m.age.90.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=74 (smallest alerting effect in the main model, in absolute value of the estimate)
m.age.74.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-74) +
                   Flanker * I(Age-74) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.74.raw), cor=F)
cbind(summary(m.age.74.raw)$coefficients, p.lmer(m.age.74.raw))
confint(m.age.74.raw, parm="Cue.ALERTING")

## Baseline: Age=73 (smallest alerting effect for raw model, in absolute value of the estimate)
m.age.73.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-73) +
                   Flanker * I(Age-73) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.73.raw), cor=F)
cbind(summary(m.age.73.raw)$coefficients, p.lmer(m.age.73.raw))
confint(m.age.73.raw, parm="Cue.ALERTING")

## Under 90
m.age.u90.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main[ant.main$Age<90,])
print(summary(m.age.u90.raw), cor=F)
cbind(summary(m.age.u90.raw)$coefficients, p.lmer(m.age.u90.raw), confint(m.age.u90.raw, parm="beta_"))
```

```{r}
#| label: Senitivity Analysis for the Main Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.main$Participant.RT.log <- ave(log(ant.main$RT), list(ant.main$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.main)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.main)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.main[!is.na(ant.main$Visual_Acuity), ])
length(unique(ant.main[!is.na(ant.main$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.main[!is.na(ant.main$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.main[ant.main$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.main[ant.main$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.main[ant.main$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.main[ant.main$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50 <- droplevels(ant[ant$Cue!="DOUBLE" & ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50$Sex <- factor(ant.acc50$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50$Sex) <- matrix(dimnames=list(levels(ant.acc50$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50$Flanker <- factor(ant.acc50$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50$Flanker) <- matrix(dimnames=list(levels(ant.acc50$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50$Cue <- factor(ant.acc50$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50$Cue) <- matrix(dimnames=list(levels(ant.acc50$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.main[ant.main$AccuracyAtLeast90==1,])
length(unique(ant.main[ant.main$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.main[ant.main$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.main[ant.main$Age<90,])
length(unique(ant.main[ant.main$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.main[ant.main$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))
```

## Combined Baseline (Log and Raw RT)

This section is for the combined baseline models (Log and Raw RT). In this case the central cue and double cue have been combined, by the way of re-coding double as central. This code had to be corrected in order to obtain reported findings. Note the mistake was in the subset part of this section related to the re-coding of the cues. Another point to be noted is that @veríssimo2022 state that this model is only applicable for alerting and conflict measures. $$Alerting = NoCue - Combined$$ $$Orienting = Combined - Spatial$$ $$Conflict = Incongruent - Congruent$$

```{r}
#| label: Subset data for Linear combined Model

# Subset (excluded: participants less than 75% accuracy, incorrect responses)
## Data points and n of participants with central and double cues
nrow(ant.combined <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Accuracy==1,]))
length(unique(ant.combined$Participant_ID))
# Recode DOUBLE are CENTRAL
ant.combined$Cue <- factor(ant.combined$Cue, levels = c("CENTRAL", "DOUBLE", "NOCUE", "SPATIAL"))
levels(ant.combined$Cue)[levels(ant.combined$Cue)=="DOUBLE"] <- "CENTRAL"
# Contrasts (for Sex, Flanker, and Cue)
ant.combined$Sex <- factor(ant.combined$Sex, levels=c("Female", "Male"))
(contrasts(ant.combined$Sex) <- matrix(dimnames=list(levels(ant.combined$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.combined$Flanker <- factor(ant.combined$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.combined$Flanker) <- matrix(dimnames=list(levels(ant.combined$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.combined$Cue <- factor(ant.combined$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.combined$Cue) <- matrix(dimnames=list(levels(ant.combined$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear combined Models and Follow-ups (Log and Raw RT)

# Combined Model (Log RT)
m.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * c.(Age) +
                   Flanker * c.(Age) +
                   Sex + c.(Education) + c.(Trial),
                 ant.combined)
print(summary(m.combined), cor=F)
cbind(summary(m.combined)$coefficients, p.lmer(m.combined), confint(m.combined, parm="beta_"))

# Combined Model (Raw RT)
m.combined.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * c.(Age) +
                   Flanker * c.(Age) +
                   Sex + c.(Education) + c.(Trial),
                 ant.combined)
print(summary(m.combined.raw), cor=F)
cbind(summary(m.combined.raw)$coefficients, p.lmer(m.combined.raw), confint(m.combined.raw, parm="beta_"))
```

```{r}
#| label: Senitivity Analysis for the Combined Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.combined$Participant.RT.log <- ave(log(ant.combined$RT), list(ant.combined$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.combined)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.combined)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.combined[!is.na(ant.combined$Visual_Acuity), ])
length(unique(ant.combined[!is.na(ant.combined$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.combined[!is.na(ant.combined$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.combined[ant.combined$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined[ant.combined$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.combined[ant.combined$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined[ant.combined$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50.combined <- droplevels(ant[ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50.combined$Cue <- factor(ant.acc50.combined$Cue, levels = c("CENTRAL", "DOUBLE", "NOCUE", "SPATIAL"))
levels(ant.acc50.combined$Cue)[levels(ant.acc50.combined$Cue)=="DOUBLE"] <- "CENTRAL"
ant.acc50.combined$Sex <- factor(ant.acc50.combined$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50.combined$Sex) <- matrix(dimnames=list(levels(ant.acc50.combined$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50.combined$Flanker <- factor(ant.acc50.combined$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50.combined$Flanker) <- matrix(dimnames=list(levels(ant.acc50.combined$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50.combined$Cue <- factor(ant.acc50.combined$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50.combined$Cue) <- matrix(dimnames=list(levels(ant.acc50.combined$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50.combined)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.combined[ant.combined$AccuracyAtLeast90==1,])
length(unique(ant.combined[ant.combined$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.combined[ant.combined$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.combined[ant.combined$Age<90,])
length(unique(ant.combined[ant.combined$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.combined[ant.combined$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))
```

## Double Baseline (Log and Raw RT)

The code for the double baseline models are in the following blocks. In these models the central cue was substituted with the double cue instead. Although @veríssimo2022 have not considered this baseline for analysis in their study, this is the recommended baseline by @fan2009, whom @veríssimo2022 base their ANT paradigm on with their work in 2005.\
$$Alerting = NoCue - Double$$ $$Orienting = Double - Spatial$$ $$Conflict = Incongruent - Congruent$$

```{r}
#| label: Subset data for Linear Double Model

# Subset (excluded: participants less than 75% accuracy, incorrect responses, double cue trials)
nrow(ant.double <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Cue!="CENTRAL" & ant$Accuracy==1,]))
length(unique(ant.double$Participant_ID))
# Contrasts (for Sex, Flanker, and Cue)
ant.double$Sex <- factor(ant.double$Sex, levels=c("Female", "Male"))
(contrasts(ant.double$Sex) <- matrix(dimnames=list(levels(ant.double$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.double$Flanker <- factor(ant.double$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.double$Flanker) <- matrix(dimnames=list(levels(ant.double$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.double$Cue <- factor(ant.double$Cue, levels=c("DOUBLE", "NOCUE", "SPATIAL"))
(contrasts(ant.double$Cue) <- matrix(dimnames=list(levels(ant.double$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear Double Models and Follow-ups (Log and Raw RT)

# Double Model (Log RT)
m.double <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                     Cue * Flanker +
                     Cue * c.(Age) +
                     Flanker * c.(Age) +
                     Sex + c.(Education) + c.(Trial),
                   ant.double)
print(summary(m.double), cor = FALSE)
cbind(summary(m.double)$coefficients, p.lmer(m.double), confint(m.double, parm = "beta_"))

# Double Model (Raw RT) 
m.double.raw <- lmer(RT ~ (1 + Flanker | Participant_ID) +
                     Cue * Flanker +
                     Cue * c.(Age) +
                     Flanker * c.(Age) +
                     Sex + c.(Education) + c.(Trial),
                   ant.double)
print(summary(m.double.raw), cor = FALSE)
cbind(summary(m.double.raw)$coefficients, p.lmer(m.double.raw), confint(m.double.raw, parm = "beta_"))

```

```{r}
#| label: Senitivity Analysis for the Double Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.double$Participant.RT.log <- ave(log(ant.double$RT), list(ant.double$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.double)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.double)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.double[!is.na(ant.double$Visual_Acuity), ])
length(unique(ant.double[!is.na(ant.double$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.double[!is.na(ant.double$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.double[ant.double$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.double[ant.double$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.double[ant.double$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.double[ant.double$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50.double <- droplevels(ant[ant$Cue!="CENTRAL" & ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50.double$Sex <- factor(ant.acc50.double$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50.double$Sex) <- matrix(dimnames=list(levels(ant.acc50.double$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50.double$Flanker <- factor(ant.acc50.double$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50.double$Flanker) <- matrix(dimnames=list(levels(ant.acc50.double$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50.double$Cue <- factor(ant.acc50.double$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50.double$Cue) <- matrix(dimnames=list(levels(ant.acc50.double$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50.double)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.double[ant.double$AccuracyAtLeast90==1,])
length(unique(ant.double[ant.double$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.double[ant.double$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.double[ant.double$Age<90,])
length(unique(ant.double[ant.double$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.double[ant.double$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

```

## Quadratic Model

This section holds the code for the replication and the robustness for the quadratic model used by @veríssimo2022. Please view the supplementary for more information about the model, but in short a quadratic term is added to age in order to explain their effects further.

```{r}
#| label: Quadratic Models

# main model (log RT)
m.quad <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.main)
print(summary(m.quad), cor=F)
cbind(summary(m.quad)$coefficients, p.lmer(m.quad))
confint(m.quad, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# main model (raw RT)
m.quad.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.main)
print(summary(m.quad.raw), cor=F)
cbind(summary(m.quad.raw)$coefficients, p.lmer(m.quad.raw))
confint(m.quad.raw, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# double cue model (log RT)
m.quad.double <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.double)
print(summary(m.quad.double), cor=F)
cbind(summary(m.quad.double)$coefficients, p.lmer(m.quad.double))
confint(m.quad.double, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# combined model (log RT)
m.quad.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined)
print(summary(m.quad.combined), cor=F)
cbind(summary(m.quad.combined)$coefficients, p.lmer(m.quad.combined))
confint(m.quad.combined, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

```

## Bi-Linear Model

This model is known as the breakpoint model in @veríssimo2022. The code is present for all three baselines along with the figure with the AIC plot.

```{r}
#| label: Bilinear Model (Log and Raw RT) 

# Main Modle (Log RT)
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.fit <- NULL

for(bp in seq(min(ant.main$Age), max(ant.main$Age), 1)){
  ant.main$adj.Age <- ant.main$Age - bp
  ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)
  m.current <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp) +
                      Flanker * (adj.Age + adj.Age:post.bp) +
                      Sex + c.(Education) + c.(Trial),
                    ant.main, REML=F)
  m.current.fit <- data.frame(Breakpoint=bp, Deviance=deviance(m.current, REML=F), AIC=AIC(m.current))
models.fit <- rbind(models.fit, m.current.fit)}

# Best breakpoint
models.fit[models.fit$AIC==min(models.fit$AIC),]
bp <- models.fit[models.fit$AIC==min(models.fit$AIC),]$Breakpoint

# Make indicator variable
ant.main$adj.Age <- ant.main$Age - bp
ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)

# Model
m.break <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp) +
                  Flanker * (adj.Age + adj.Age:post.bp) +
                  Sex + c.(Education) + c.(Trial),
                ant.main)
print(summary(m.break), cor=F)
cbind(summary(m.break)$coefficients, p.lmer(m.break))
confint(m.break, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.fit$deltaAIC <- models.fit$AIC - min(models.fit$AIC)

ggplot(models.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint (Log RT) Search Using AIC"
    ) +
    theme_classic()

# Main Model (Raw RT)
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.fit.raw <- NULL

for(bp in seq(min(ant.main$Age), max(ant.main$Age), 1)){
  ant.main$adj.Age <- ant.main$Age - bp
  ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)
  m.current.raw <- lmer(RT ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp) +
                      Flanker * (adj.Age + adj.Age:post.bp) +
                      Sex + c.(Education) + c.(Trial),
                    ant.main, REML=F)
  m.current.fit.raw <- data.frame(Breakpoint=bp, Deviance=deviance(m.current.raw, REML=F), AIC=AIC(m.current.raw))
models.fit.raw <- rbind(models.fit.raw, m.current.fit.raw)}

# Best breakpoint
models.fit.raw[models.fit.raw$AIC==min(models.fit.raw$AIC),]
bp.raw <- models.fit.raw[models.fit.raw$AIC==min(models.fit.raw$AIC),]$Breakpoint

# Make indicator variable
ant.main$adj.Age <- ant.main$Age - bp
ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)

# Model
m.break.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp) +
                  Flanker * (adj.Age + adj.Age:post.bp) +
                  Sex + c.(Education) + c.(Trial),
                ant.main)
print(summary(m.break.raw), cor=F)
cbind(summary(m.break.raw)$coefficients, p.lmer(m.break.raw))
confint(m.break.raw, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.fit.raw$deltaAIC <- models.fit.raw$AIC - min(models.fit.raw$AIC)

ggplot(models.fit.raw, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint (Raw RT) Search Using AIC"
    ) +
    theme_classic()

# Double Model
models.double.fit <- NULL

for(bp.d in seq(min(ant.double$Age), max(ant.double$Age), 1)){
  ant.double$adj.Age <- ant.double$Age - bp.d
  ant.double$post.bp.d <- as.numeric(ant.double$adj.Age>0)
  m.current.double <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp.d) +
                      Flanker * (adj.Age + adj.Age:post.bp.d) +
                      Sex + c.(Education) + c.(Trial),
                    ant.double, REML=F)
  m.current.double.fit <- data.frame(Breakpoint=bp.d, Deviance=deviance(m.current.double, REML=F), AIC=AIC(m.current.double))
models.double.fit <- rbind(models.double.fit, m.current.double.fit)}

# Best breakpoint
models.double.fit[models.double.fit$AIC==min(models.double.fit$AIC),]
bp.d <- models.double.fit[models.double.fit$AIC==min(models.double.fit$AIC),]$Breakpoint

# Make indicator variable
ant.double$adj.Age <- ant.double$Age - bp.d
ant.double$post.bp.d <- as.numeric(ant.double$adj.Age>0)

# Model
m.break.double <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp.d) +
                  Flanker * (adj.Age + adj.Age:post.bp.d) +
                  Sex + c.(Education) + c.(Trial),
                ant.double)
print(summary(m.break.double), cor=F)
cbind(summary(m.break.double)$coefficients, p.lmer(m.break.double))
confint(m.break.double, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.double.fit$deltaAIC <- models.double.fit$AIC - min(models.double.fit$AIC)

ggplot(models.double.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp.d, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint Double (Log RT) Search Using AIC"
    ) +
    theme_classic()

# Combined Model
models.combined.fit <- NULL

for(bp.c in seq(min(ant.combined$Age), max(ant.combined$Age), 1)){
  ant.combined$adj.Age <- ant.combined$Age - bp.c
  ant.combined$post.bp.c <- as.numeric(ant.combined$adj.Age>0)
  m.current.combined <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp.c) +
                      Flanker * (adj.Age + adj.Age:post.bp.c) +
                      Sex + c.(Education) + c.(Trial),
                    ant.combined, REML=F)
  m.current.combined.fit <- data.frame(Breakpoint=bp.c, Deviance=deviance(m.current.combined, REML=F), AIC=AIC(m.current.combined))
models.combined.fit <- rbind(models.combined.fit, m.current.combined.fit)}

# Best breakpoint
models.combined.fit[models.combined.fit$AIC==min(models.combined.fit$AIC),]
bp.c <- models.combined.fit[models.combined.fit$AIC==min(models.combined.fit$AIC),]$Breakpoint

# Make indicator variable
ant.combined$adj.Age <- ant.combined$Age - bp.c
ant.combined$post.bp.c <- as.numeric(ant.combined$adj.Age>0)

# Model
m.break.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp.c) +
                  Flanker * (adj.Age + adj.Age:post.bp.c) +
                  Sex + c.(Education) + c.(Trial),
                ant.combined)
print(summary(m.break.combined), cor=F)
cbind(summary(m.break.combined)$coefficients, p.lmer(m.break.combined))
confint(m.break.combined, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.combined.fit$deltaAIC <- models.combined.fit$AIC - min(models.combined.fit$AIC)

ggplot(models.combined.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp.c, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint combined (Log RT) Search Using AIC"
    ) +
    theme_classic()
```

# Reliability

For the purposes of reliability we have chosen Spearman Brown Intraclass Correlation Coefficient (S-B). This has been run as a split-half with 10000 permutations as done by prior literature [@ishigami2013]

```{r}
#| label: Multi Permutation Correlation Reliability ICC
set.seed(1996)

n_perm <- 10000
exec_corrs <- numeric(n_perm)
alert_corrs <- numeric(n_perm)
orient_corrs <- numeric(n_perm)
alert_d_corrs <- numeric(n_perm)

# Alerting
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Alerting network score
  alert_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Alert_Net = RT[Cue == "NOCUE"] -
                 RT[Cue == "CENTRAL"],
      .groups = "drop"
    )

  alert_gutt_random <- alert_score_random |>
    pivot_wider(names_from = split, values_from = Alert_Net)

  # Split-half correlation
  alert_corrs[i] <- icc(alert_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}

alert_corrs_SB <- (2 * alert_corrs) / (1 + alert_corrs)
alert_est <- median(alert_corrs_SB, na.rm = TRUE)
alert_CI <- quantile(alert_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(alert_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Executive
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Flanker) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Executive network score
  exec_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Flanker) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Exec_Net = RT[Flanker == "INCONGRUENT"] -
                 RT[Flanker == "CONGRUENT"],
      .groups = "drop"
    )

  exec_gutt_random <- exec_score_random |>
    pivot_wider(names_from = split, values_from = Exec_Net)

  # Split-half correlation
  exec_corrs[i] <- icc(exec_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
exec_corrs_SB <- (2 * exec_corrs) / (1 + exec_corrs)
exec_est <- median(exec_corrs_SB, na.rm = TRUE)
exec_CI <- quantile(exec_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(exec_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Orienting
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Orienting network score
  orient_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Orient_Net = RT[Cue == "CENTRAL"] -
                 RT[Cue == "SPATIAL"],
      .groups = "drop"
    )

  orient_gutt_random <- orient_score_random |>
    pivot_wider(names_from = split, values_from = Orient_Net)

  # Split-half correlation
  orient_corrs[i] <- icc(orient_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
orient_corrs_SB <- (2 * orient_corrs) / (1 + orient_corrs)
orient_est <- median(orient_corrs_SB, na.rm = TRUE)
orient_CI <- quantile(orient_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(orient_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Alerting Double
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Alerting network score
  alert_d_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Alert_Net = RT[Cue == "NOCUE"] -
                 RT[Cue == "DOUBLE"],
      .groups = "drop"
    )

  alert_d_gutt_random <- alert_d_score_random |>
    pivot_wider(names_from = split, values_from = Alert_Net)

  # Split-half correlation
  alert_d_corrs[i] <- icc(alert_d_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
alert_d_corrs_SB <- (2 * alert_d_corrs) / (1 + alert_d_corrs)
alert_d_est <- median(alert_d_corrs_SB, na.rm = TRUE)
alert_d_CI <- quantile(alert_d_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)

hist(alert_d_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")
```

# Correlation

For the sake of completeness we have added the correlation between the different ANT measures and the Age. This is done in an attempt to learn the relationship between the measures when calculated with different baselines.

```{r}
#| label: ANT Measure and Age Correlations

# Conflict
con.corr.m <- ant.main |>
  group_by(Participant_ID, Flanker) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Con_M" := RT[Flanker == "INCONGRUENT"] - 
              RT[Flanker == "CONGRUENT"])
con.corr.d <- ant.double |>
  group_by(Participant_ID, Flanker) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Con_D" := RT[Flanker == "INCONGRUENT"] - 
              RT[Flanker == "CONGRUENT"])
con.corr.c <- ant.combined |>
  group_by(Participant_ID, Flanker) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Con_C" := RT[Flanker == "INCONGRUENT"] - 
              RT[Flanker == "CONGRUENT"])
con.corr.all <- left_join(con.corr.m, con.corr.d, by = "Participant_ID") |> 
  left_join(con.corr.c, by = "Participant_ID")

# Alerting
alert.corr.m <- ant.main |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Alt_M" := RT[Cue == "NOCUE"] - 
              RT[Cue == "CENTRAL"])
alert.corr.d <- ant.double |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Alt_D" := RT[Cue == "NOCUE"] - 
              RT[Cue == "DOUBLE"])
alert.corr.c <- ant.combined |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Alt_C" := RT[Cue == "NOCUE"] - 
              RT[Cue == "CENTRAL"])
alert.corr.all <- left_join(alert.corr.m, alert.corr.d, by = "Participant_ID") |> 
  left_join(alert.corr.c, by = "Participant_ID")

# Orienting
orient.corr.m <- ant.main |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Ori_M" := RT[Cue == "CENTRAL"] - 
              RT[Cue == "SPATIAL"])
orient.corr.d <- ant.double |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Ori_D" := RT[Cue == "DOUBLE"] - 
              RT[Cue == "SPATIAL"])
orient.corr.c <- ant.combined |>
  group_by(Participant_ID, Cue) |>
  summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
  group_by(Participant_ID) |>
  summarise("Ori_C" := RT[Cue == "CENTRAL"] - 
              RT[Cue == "SPATIAL"])
orient.corr.all <- left_join(orient.corr.m, orient.corr.d, by = "Participant_ID") |> 
  left_join(orient.corr.c, by = "Participant_ID")

# Age
ant.age <- ant.main
ant.age <- subset(ant.age, select = c("Participant_ID", "Age"))
ant.age <- unique(ant.age)

net.corr <- left_join(alert.corr.all, orient.corr.all, by = "Participant_ID") |>
  left_join(con.corr.all, by = "Participant_ID") |> left_join(ant.age, by = "Participant_ID")

measure.age.cor <- corr.test(net.corr[, -1], 
                        use = "pairwise", 
                        method = "pearson", 
                        adjust = "holm",
                        ci = TRUE)
measure.corr.table <- cbind(measure.age.cor$r, measure.age.cor$n, measure.age.cor$p)
colnames(measure.corr.table) <- c(colnames(measure.age.cor$r), "n", colnames(measure.age.cor$p))

corrplot(measure.age.cor$r, method = "number", 
         type = "upper", order = "hclust",
         addCoef.col = "black", tl.col = "black",
         tl.srt = 45, p.mat = measure.age.cor$p, 
         sig.level = c(.001, .01, .05), insig = "label_sig")
corrplot(measure.age.cor$r, method = "number", 
         type = "upper", order = "hclust",
         addCoef.col = "black", tl.col = "black",
         tl.srt = 45, p.mat = measure.age.cor$p, number.digits = 3)
```

# Figures

## Linear Figures

@veríssimo2022 have not provided the code to reproduce their figures. We have created approximations for them. The code required to reproduce our figure is also provided in the code block.

```{r}
#| label: Figures for easy comparison

# Main Model
## Alerting 
ant.alert.main <- droplevels(ant.main[ant.main$Cue != "SPATIAL",])
ant.alert <- ant.alert.main |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.alert <- ant.alert |> 
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.alert <- ant.alert |>
  mutate(difference = log(NOCUE) - log(CENTRAL))
alert.age <- ant.alert.main |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.alert <- ant.alert |>
  left_join(alert.age, by = "Participant_ID")
## Orienting Model
ant.orient.main <- droplevels(ant.main[ant.main$Cue != "NOCUE",])
ant.orient <- ant.orient.main |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE, .groups = "drop"))
ant.orient <- ant.orient |>
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.orient <- ant.orient |>
  mutate(difference = log(CENTRAL) - log(SPATIAL))
orient.age <- ant.orient.main |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.orient <- ant.orient |>
  left_join(orient.age, by = "Participant_ID")
## Executive Model
ant.exec.main <- ant.main|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec <- ant.exec.main |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec <- ant.exec |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age <- ant.main |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec <- ant.exec |>
  left_join(exec.age, by = "Participant_ID")

# Combined Model
## Alerting
ant.alert.combined <- droplevels(ant.combined[ant.combined$Cue != "SPATIAL",])
ant.alert.c <- ant.alert.combined |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.alert.c <- ant.alert.c |> 
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.alert.c <- ant.alert.c |>
  mutate(difference = log(NOCUE) - log(CENTRAL))
alert.age.c <- ant.alert.combined |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.alert.c <- ant.alert.c |>
  left_join(alert.age.c, by = "Participant_ID")
#Orienting combined Model
ant.orient.combined <- droplevels(ant.combined[ant.combined$Cue != "NOCUE",])
ant.orient.c <- ant.orient.combined |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE, .groups = "drop"))
ant.orient.c <- ant.orient.c |>
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.orient.c <- ant.orient.c |>
  mutate(difference = log(CENTRAL) - log(SPATIAL))
orient.age.c <- ant.orient.combined |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.orient.c <- ant.orient.c |>
  left_join(orient.age.c, by = "Participant_ID")
#Executive combined Model
ant.exec.combined <- ant.combined|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec.c <- ant.exec.combined |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec.c <- ant.exec.c |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age.c <- ant.combined |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec.c <- ant.exec.c |>
  left_join(exec.age.c, by = "Participant_ID")

# Double Model
## Alerting 
ant.alert.double <- droplevels(ant.double[ant.double$Cue != "SPATIAL",])
ant.alert.d <- ant.alert.double |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.alert.d <- ant.alert.d |> 
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.alert.d <- ant.alert.d |>
  mutate(difference = log(NOCUE) - log(DOUBLE))
alert.age.d <- ant.alert.double |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.alert.d <- ant.alert.d |>
  left_join(alert.age.d, by = "Participant_ID")
## Orienting 
ant.orient.double <- droplevels(ant.double[ant.double$Cue != "NOCUE",])
ant.orient.d <- ant.orient.double |> group_by(Participant_ID, Cue) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE, .groups = "drop"))
ant.orient.d <- ant.orient.d |>
  pivot_wider(names_from = Cue, values_from = Mean_RT)
ant.orient.d <- ant.orient.d |>
  mutate(difference = log(DOUBLE) - log(SPATIAL))
orient.age.d <- ant.orient.double |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.orient.d <- ant.orient.d |>
  left_join(orient.age.d, by = "Participant_ID")
## Executive 
ant.exec.double <- ant.double|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec.d <- ant.exec.double |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec.d <- ant.exec.d |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age.d <- ant.double |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec.d <- ant.exec.d |>
  left_join(exec.age.d, by = "Participant_ID")

# Alerting Plot
plot_alerting<- ggplot() +
  geom_point(data = ant.alert, aes(Age, difference, color = "Central"), alpha = 0.02) + 
  geom_smooth(data = ant.alert, aes(Age, difference, color = "Central"), method = "lm", se = FALSE) + 
  geom_point(data = ant.alert.c, aes(Age, difference, color = "Combined"), alpha = 0.02) + 
  geom_smooth(data = ant.alert.c, aes(Age, difference, color = "Combined"), method = "lm", se = FALSE) + 
  geom_point(data = ant.alert.d, aes(Age, difference, color = "Double"), alpha = 0.02) + 
  geom_smooth(data = ant.alert.d, aes(Age, difference, color = "Double"), method = "lm", se = FALSE) + 
  scale_y_continuous(limits = c(-0.4, 0.4)) +
  scale_color_npg(name = "Baseline") +
  labs(
    title = "Age Interaction with Alerting",
    x = "Age (years)",
    y = "log-RT difference",
    color = "Group",
    caption = "Note: ** =  p < .01, * = p < .05"
  ) +
    theme(plot.title = element_text(hjust = 0.5, size = rel(1.2), face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = rel(1), color = "grey40"),
        plot.caption = element_text(hjust = 1, size = rel(0.8), color = "grey50"),
        axis.title = element_text(face = "bold", size = rel(1)),
        axis.text = element_text(color = "black", size = rel(0.9)),
        axis.line = element_line(linewidth = 0.5, color = "black"),
        axis.ticks = element_line(linewidth = 0.5, color = "black"),
        axis.ticks.length = unit(0.2, "mm"),
        legend.title = element_text(size = rel(1), face = "bold"),
        legend.text = element_text(size = rel(0.9)),
        legend.key.size = unit(0.8, "cm"),
        legend.position = c(0.9, 0.9),
        legend.margin = margin(2, 2, 2, 2),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        plot.margin = margin(5, 10, 5, 5, "pt"),
        panel.background = element_blank()) + 
  coord_cartesian(clip = "off")

lm_central <- lm(difference ~ Age, data = ant.alert)
lm_combined <- lm(difference ~ Age, data = ant.alert.c)
end_age_central <- max(ant.alert$Age)
end_age_combined <- max(ant.alert.c$Age)
end_pred_central <- predict(lm_central, newdata = data.frame(Age = end_age_central))
end_pred_combined <- predict(lm_combined, newdata = data.frame(Age = end_age_combined))

plot_alerting <- plot_alerting +
  annotate("text", 
           x = end_age_central + 0.1,        
           y = end_pred_central - 0.01,            
           label = "**", 
           color = "#E64B35",
           size = 4, fontface = "bold", hjust = 0)
plot_alerting <- plot_alerting +
  annotate("text",
           x = end_age_combined + 0.1,
           y = end_pred_combined - 0.005,
           label = "*",
           color = "#4DBBD5",
           size = 4, fontface = "bold", hjust = 0)
plot_alerting <- plot_alerting +
  annotate("text",
           x = -Inf,
           y = -0.4,
           label = "\u2193 Worse",
           hjust = -0.1,
           vjust = 0,
           size = 3.5,
           fontface = "italic") +
  annotate("text",
           x = -Inf,
           y = 0.4,
           label = "\u2191 Better",
           hjust = -0.1,
           vjust = 1,
           size = 3.5,
           fontface = "italic")

# Orienting Plot
plot_orienting<- ggplot() +
  geom_point(data = ant.orient, aes(Age, difference, color = "Central"), alpha = 0.05) + 
  geom_smooth(data = ant.orient, aes(Age, difference, color = "Central"), method = "lm", se = FALSE) + 
  geom_point(data = ant.orient.c, aes(Age, difference, color = "Combined"), alpha = 0.05) + 
  geom_smooth(data = ant.orient.c, aes(Age, difference, color = "Combined"), method = "lm", se = FALSE) + 
  geom_point(data = ant.orient.d, aes(Age, difference, color = "Double"), alpha = 0.05) + 
  geom_smooth(data = ant.orient.d, aes(Age, difference, color = "Double"), method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-0.25, 0.25)) +
  scale_color_npg(name = "Baseline") +
  labs(
    title = "Orienting",
    x = "Age (years)",
    y = "log-RT difference",
    color = "Group",
    caption = "Note: ** =  p < .01, * = p < .05"
  ) +
  theme(plot.title = element_text(hjust = 0.5, size = rel(1.2), face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = rel(1), color = "grey40"),
        plot.caption = element_text(hjust = 1, size = rel(0.8), color = "grey50"),
        axis.title = element_text(face = "bold", size = rel(1)),
        axis.text = element_text(color = "black", size = rel(0.9)),
        axis.line = element_line(linewidth = 0.5, color = "black"),
        axis.ticks = element_line(linewidth = 0.5, color = "black"),
        axis.ticks.length = unit(2, "mm"),
        legend.title = element_text(size = rel(1), face = "bold"),
        legend.text = element_text(size = rel(0.9)),
        legend.key.size = unit(0.8, "cm"),
        legend.position = c(0.9, 0.9),
        legend.margin = margin(2, 2, 2, 2),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        plot.margin = margin(5, 10, 5, 5, "pt"),
        panel.background = element_blank()) + 
  coord_cartesian(clip = "off")

lm_central <- lm(difference ~ Age, data = ant.orient)
lm_combined <- lm(difference ~ Age, data = ant.orient.c)
end_age_central <- max(ant.orient$Age)
end_age_combined <- max(ant.orient.c$Age)
end_pred_central <- predict(lm_central, newdata = data.frame(Age = end_age_central))
end_pred_combined <- predict(lm_combined, newdata = data.frame(Age = end_age_combined))

plot_orienting <- plot_orienting +
  annotate("text", 
           x = end_age_central + 0.1,        
           y = end_pred_central + 0.0001,            
           label = "**", 
           color = "#E64B35",
           size = 4, fontface = "bold", hjust = 0)
plot_orienting <- plot_orienting +
  annotate("text",
           x = end_age_combined + 0.1,
           y = end_pred_combined - 0.0005,
           label = "*",
           color = "#4DBBD5",
           size = 4, fontface = "bold", hjust = 0)
plot_orienting <- plot_orienting +
  annotate("text",
           x = -Inf,
           y = -0.25,
           label = "\u2193 Worse",
           hjust = -0.1,
           vjust = 0,
           size = 3.5,
           fontface = "italic") +
  annotate("text",
           x = -Inf,
           y = 0.25,
           label = "\u2191 Better",
           hjust = -0.1,
           vjust = 1,
           size = 3.5,
           fontface = "italic")

# Conflict Plot
plot_executive<- ggplot() +
  geom_point(data = ant.exec, aes(Age, difference, color = "Central"), alpha = 0.02) + 
  geom_smooth(data = ant.exec, aes(Age, difference, color = "Central"), method = "lm", se = FALSE) + 
  geom_point(data = ant.exec.c, aes(Age, difference, color = "Combined"), alpha = 0.02) + 
  geom_smooth(data = ant.exec.c, aes(Age, difference, color = "Combined"), method = "lm", se = FALSE) + 
  geom_point(data = ant.exec.d, aes(Age, difference, color = "Double"), alpha = 0.02) + 
  geom_smooth(data = ant.exec.d, aes(Age, difference, color = "Double"), method = "lm", se = FALSE) +
  scale_y_continuous(limits = c(-0.3, 0.3)) +
  scale_color_npg(name = "Baseline") +
  labs(
    title = "Age Interaction with Conflict Avoidance",
    x = "Age (years)",
    y = "log-RT difference",
    color = "Group",
    caption = "Note: All baselines are significant at p < .001"
  ) +
  theme(plot.title = element_text(hjust = 0.5, size = rel(1.2), face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = rel(1), color = "grey40"),
        plot.caption = element_text(hjust = 1, size = rel(0.8), color = "grey50"),
        axis.title = element_text(face = "bold", size = rel(1)),
        axis.text = element_text(color = "black", size = rel(0.9)),
        axis.line = element_line(linewidth = 0.5, color = "black"),
        axis.ticks = element_line(linewidth = 0.5, color = "black"),
        axis.ticks.length = unit(0.2, "mm"),
        legend.title = element_text(size = rel(1), face = "bold"),
        legend.text = element_text(size = rel(0.9)),
        legend.key.size = unit(0.8, "cm"),
        legend.position = c(0.9, 0.9),
        legend.margin = margin(2, 2, 2, 2),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        plot.margin = margin(5, 10, 5, 5, "pt"),
        panel.background = element_blank()) + 
  coord_cartesian(clip = "off")
plot_executive <- plot_executive +
  annotate("text",
           x = -Inf,
           y = -0.3,
           label = "\u2193 Better",
           hjust = -0.1,
           vjust = 0,
           size = 3.5,
           fontface = "italic") +
  annotate("text",
           x = -Inf,
           y = 0.3,
           label = "\u2191 Worse",
           hjust = -0.1,
           vjust = 1,
           size = 3.5,
           fontface = "italic")

ggsave("Orienting_x_Age.tiff", plot_orienting, 
       width = 6.5, height = 7.5, units = "in", 
       dpi = 600, compression = "lzw", bg = "white")
ggsave("Orienting_x_Age.png", plot_orienting, 
       width = 6.5, height = 7.5, units = "in", 
       dpi = 600)
ggsave("Alerting_x_Age.png", plot_alerting, 
       width = 6.5, height = 7.5, units = "in", 
       dpi = 600)
ggsave("Conflict_x_Age.png", plot_executive, 
       width = 6.5, height = 7.5, units = "in", 
       dpi = 600)
```

## Quadratic Figures

```{r}
#| label: Figures for easy comparison

# Main Model
## Executive Model
ant.exec.main <- ant.main|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec <- ant.exec.main |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec <- ant.exec |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age <- ant.main |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec <- ant.exec |>
  left_join(exec.age, by = "Participant_ID")

# Combined Model
#Executive combined Model
ant.exec.combined <- ant.combined|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec.c <- ant.exec.combined |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec.c <- ant.exec.c |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age.c <- ant.combined |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec.c <- ant.exec.c |>
  left_join(exec.age.c, by = "Participant_ID")

# Double Model
## Executive 
ant.exec.double <- ant.double|> group_by(Participant_ID, Flanker) |>
  summarise(Mean_RT = mean(RT, na.rm = TRUE), .groups = "drop")
ant.exec.d <- ant.exec.double |>
  pivot_wider(names_from = Flanker, values_from = Mean_RT)
ant.exec.d <- ant.exec.d |>
  mutate(difference = log(INCONGRUENT) - log(CONGRUENT))
exec.age.d <- ant.double |>
  select(Participant_ID, Age) |>
  distinct(Participant_ID, .keep_all = TRUE)
ant.exec.d <- ant.exec.d |>
  left_join(exec.age.d, by = "Participant_ID")

# Conflict Plot
plot_executive_q<- ggplot() +
  geom_point(data = ant.exec, aes(Age, difference, color = "Central"), alpha = 0.02) + 
  geom_smooth(data = ant.exec, aes(Age, difference, color = "Central"), method = "lm", formula = y ~ poly(x, 2), se = FALSE) + 
  geom_point(data = ant.exec.c, aes(Age, difference, color = "Combined"), alpha = 0.02) + 
  geom_smooth(data = ant.exec.c, aes(Age, difference, color = "Combined"), method = "lm", formula = y ~ poly(x, 2), se = FALSE) + 
  geom_point(data = ant.exec.d, aes(Age, difference, color = "Double"), alpha = 0.02) + 
  geom_smooth(data = ant.exec.d, aes(Age, difference, color = "Double"), method = "lm", formula = y ~ poly(x, 2), se = FALSE) +
  scale_y_continuous(limits = c(-0.3, 0.3)) +
  scale_color_npg(name = "Baseline") +
  labs(
    title = "Quadratic Age effects on Conflict Avoidance",
    x = "Age (years)",
    y = "log-RT difference",
    color = "Group",
    caption = "Note: ** =  p < .01, * = p < .05"
  ) +
  theme(plot.title = element_text(hjust = 0.5, size = rel(1.2), face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = rel(1), color = "grey40"),
        plot.caption = element_text(hjust = 1, size = rel(0.8), color = "grey50"),
        axis.title = element_text(face = "bold", size = rel(1)),
        axis.text = element_text(color = "black", size = rel(0.9)),
        axis.line = element_line(linewidth = 0.5, color = "black"),
        axis.ticks = element_line(linewidth = 0.5, color = "black"),
        axis.ticks.length = unit(0.2, "mm"),
        legend.title = element_text(size = rel(1), face = "bold"),
        legend.text = element_text(size = rel(0.9)),
        legend.key.size = unit(0.8, "cm"),
        legend.position = c(0.9, 0.9),
        legend.margin = margin(2, 2, 2, 2),
        panel.grid = element_blank(),
        panel.border = element_blank(),
        plot.background = element_blank(),
        plot.margin = margin(5, 10, 5, 5, "pt"),
        panel.background = element_blank()) + 
  coord_cartesian(clip = "off") 

lm_q_central <- lm(difference ~ Age, data = ant.exec)
lm_q_combined <- lm(difference ~ Age, data = ant.exec.c)
end_q_age_central <- max(ant.exec$Age)
end_q_age_combined <- max(ant.exec.c$Age)
end_q_pred_central <- predict(lm_q_central, newdata = data.frame(Age = end_q_age_central))
end_q_pred_combined <- predict(lm_q_combined, newdata = data.frame(Age = end_q_age_combined))
plot_executive_q <- plot_executive_q +
  annotate("text", 
           x = end_q_age_central + 0.1,        
           y = end_q_pred_central + 0.05,            
           label = "**", 
           color = "#E64B35",
           size = 4, fontface = "bold", hjust = 0)
plot_executive_q <- plot_executive_q +
  annotate("text", 
           x = end_q_age_combined + 0.1,        
           y = end_q_pred_combined + 0.036,            
           label = "*", 
           color = "#4DBBD5",
           size = 4, fontface = "bold", hjust = 0)
plot_executive_q <- plot_executive_q +
  annotate("text",
           x = -Inf,
           y = -0.3,
           label = "\u2193 Better",
           hjust = -0.1,
           vjust = 0,
           size = 3.5,
           fontface = "italic") +
  annotate("text",
           x = -Inf,
           y = 0.3,
           label = "\u2191 Worse",
           hjust = -0.1,
           vjust = 1,
           size = 3.5,
           fontface = "italic")


ggsave("Conflict_x_Age_Quadratic.png", plot_executive_q, 
       width = 6.5, height = 7.5, units = "in", 
       dpi = 600)
```
