---
title: "VR2022 Reproduction Script"
author: "Viplav Tuladhar & Alex O. Holcombe"
bibliography: VR2022Report.bib
csl: apa.csl
format: html
editor: visual
---

# Loading of Data/Packages

This file has all the code for the reproduction and further testing for Veríssimo et. al. (2022) The chunk below loads the packages used and the data as well.

```{r}
#| label: Package, Data and Seed information

library(dplyr); library(ggplot2); library(tidyr); library(lme4); library(psych); library(purrr); library(RColorBrewer); library(patchwork); library(irr)

set.seed(1996)

ant <- read.table("Verissimo et al/data/ANT-data.csv", sep = ",", header = TRUE, fileEncoding = "utf-8")
```

## Centering Function Code

The following code chunk reproduces the centering and p-value calculation function used in the VR2022 paper.

```{r}
#| label: centering and p-value function

# Centering
c.  <- function(x) {scale(as.numeric(x), scale=F)}
# p-values
p.lmer <- function(model){
  p.from.t <- function (tval, obs, nf){2*(1-pt(abs(tval), obs-nf))}
  msum <- summary(model)
  mts <- msum$coefficients[, "t value"]
  mdp <- msum$devcomp$dims["N"]
  mfe <- nrow(msum$coefficients)
  mps <- as.matrix(round(p.from.t(mts, mdp, mfe), 4))
  colnames(mps) <- "p value"
  return(mps)
}
```

# Models

## Main Models (For Log and Raw RTs)

The code for the reproduction of the main model (both log RT and Raw RT) and the age gated analysis is provided in this section.

```{r}
#| label: Subset data for linear modelling (main model)

#Subset (excluded: participants less than 75% accuracy, incorrect responses, double cue trials)
nrow(ant.main <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Cue!="DOUBLE" & ant$Accuracy==1,]))
length(unique(ant.main$Participant_ID))
#Contrasts (for Sex, Flanker, and Cue)
ant.main$Sex <- factor(ant.main$Sex, levels=c("Female", "Male"))
(contrasts(ant.main$Sex) <- matrix(dimnames=list(levels(ant.main$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.main$Flanker <- factor(ant.main$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.main$Flanker) <- matrix(dimnames=list(levels(ant.main$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.main$Cue <- factor(ant.main$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.main$Cue) <- matrix(dimnames=list(levels(ant.main$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear Main Models and Age Follow-ups (Log and Raw)

# Main Model (Log RT)
m <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main)
print(summary(m), cor=F)
cbind(summary(m)$coefficients, p.lmer(m), confint(m, parm="beta_"))

## Linear analysis (follow-ups)
  
## Baseline: Age=58
m.age.min <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-58) +
                    Flanker * I(Age-58) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.min), cor=F)
cbind(summary(m.age.min)$coefficients, p.lmer(m.age.min))
confint(m.age.min, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=98
m.age.max <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-98) +
                    Flanker * I(Age-98) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.max), cor=F)
cbind(summary(m.age.max)$coefficients, p.lmer(m.age.max))
confint(m.age.max, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=90
m.age.90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-90) +
                   Flanker * I(Age-90) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.90), cor=F)
cbind(summary(m.age.90)$coefficients, p.lmer(m.age.90))
confint(m.age.90, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=74 (smallest alerting effect, in absolute value of the estimate)
m.age.74 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-74) +
                   Flanker * I(Age-74) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.74), cor=F)
cbind(summary(m.age.74)$coefficients, p.lmer(m.age.74))
confint(m.age.74, parm="Cue.ALERTING")

## Under 90
m.age.u90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main[ant.main$Age<90,])
print(summary(m.age.u90), cor=F)
cbind(summary(m.age.u90)$coefficients, p.lmer(m.age.u90), confint(m.age.u90, parm="beta_"))

# Main Model (Raw RT)
  
m.raw <- lmer(RT ~ (1 + Flanker | Participant_ID) +
                    Cue * Flanker +
                    Cue * c.(Age) +
                    Flanker * c.(Age) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.raw), cor = FALSE)
cbind(summary(m.raw)$coefficients, p.lmer(m.raw), confint(m.raw, parm="beta_"))

## Raw analysis (follow-ups)
  
## Baseline: Age=58
m.age.min.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-58) +
                    Flanker * I(Age-58) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.min.raw), cor=F)
cbind(summary(m.age.min.raw)$coefficients, p.lmer(m.age.min.raw))
confint(m.age.min.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=98
m.age.max.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                    Cue * Flanker +
                    Cue * I(Age-98) +
                    Flanker * I(Age-98) +
                    Sex + c.(Education) + c.(Trial),
                  ant.main)
print(summary(m.age.max.raw), cor=F)
cbind(summary(m.age.max.raw)$coefficients, p.lmer(m.age.max.raw))
confint(m.age.max.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=90
m.age.90.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-90) +
                   Flanker * I(Age-90) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.90.raw), cor=F)
cbind(summary(m.age.90.raw)$coefficients, p.lmer(m.age.90.raw))
confint(m.age.90.raw, parm=c("Cue.ALERTING", "Cue.ORIENTING", "Flanker.EXECUTIVE"))

## Baseline: Age=74 (smallest alerting effect in the main model, in absolute value of the estimate)
m.age.74.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-74) +
                   Flanker * I(Age-74) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.74.raw), cor=F)
cbind(summary(m.age.74.raw)$coefficients, p.lmer(m.age.74.raw))
confint(m.age.74.raw, parm="Cue.ALERTING")

## Baseline: Age=73 (smallest alerting effect for raw model, in absolute value of the estimate)
m.age.73.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * I(Age-73) +
                   Flanker * I(Age-73) +
                   Sex + c.(Education) + c.(Trial),
                 ant.main)
print(summary(m.age.73.raw), cor=F)
cbind(summary(m.age.73.raw)$coefficients, p.lmer(m.age.73.raw))
confint(m.age.73.raw, parm="Cue.ALERTING")

## Under 90
m.age.u90.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
            Cue * Flanker +
            Cue * c.(Age) +
            Flanker * c.(Age) +
            Sex + c.(Education) + c.(Trial),
          ant.main[ant.main$Age<90,])
print(summary(m.age.u90.raw), cor=F)
cbind(summary(m.age.u90.raw)$coefficients, p.lmer(m.age.u90.raw), confint(m.age.u90.raw, parm="beta_"))
```

```{r}
#| label: Senitivity Analysis for the Main Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.main$Participant.RT.log <- ave(log(ant.main$RT), list(ant.main$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.main)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.main)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.main[!is.na(ant.main$Visual_Acuity), ])
length(unique(ant.main[!is.na(ant.main$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.main[!is.na(ant.main$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.main[ant.main$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.main[ant.main$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.main[ant.main$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.main[ant.main$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50 <- droplevels(ant[ant$Cue!="DOUBLE" & ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50$Sex <- factor(ant.acc50$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50$Sex) <- matrix(dimnames=list(levels(ant.acc50$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50$Flanker <- factor(ant.acc50$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50$Flanker) <- matrix(dimnames=list(levels(ant.acc50$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50$Cue <- factor(ant.acc50$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50$Cue) <- matrix(dimnames=list(levels(ant.acc50$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.main[ant.main$AccuracyAtLeast90==1,])
length(unique(ant.main[ant.main$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.main[ant.main$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.main[ant.main$Age<90,])
length(unique(ant.main[ant.main$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.main[ant.main$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))
```

## Combined Model (Log and Raw RT)

This section has the code for the combined models (Log and Raw RT) i.e. calculating alerting and orienting network using both double and central. This code has been corrected to obtain the correct findings. Point to be noted is that only the Alerting and Executive networks can be estimated using this model

```{r}
#| label: Subset data for Linear combined Model

# Subset (excluded: participants less than 75% accuracy, incorrect responses - double cue trials are kept)
## Data points and n of participants with central and double cues
nrow(ant.combined <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Accuracy==1,]))
length(unique(ant.combined$Participant_ID))
# Recode DOUBLE are CENTRAL
ant.combined$Cue <- factor(ant.combined$Cue, levels = c("CENTRAL", "DOUBLE", "NOCUE", "SPATIAL"))
levels(ant.combined$Cue)[levels(ant.combined$Cue)=="DOUBLE"] <- "CENTRAL"
# Contrasts (for Sex, Flanker, and Cue)
ant.combined$Sex <- factor(ant.combined$Sex, levels=c("Female", "Male"))
(contrasts(ant.combined$Sex) <- matrix(dimnames=list(levels(ant.combined$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.combined$Flanker <- factor(ant.combined$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.combined$Flanker) <- matrix(dimnames=list(levels(ant.combined$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.combined$Cue <- factor(ant.combined$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.combined$Cue) <- matrix(dimnames=list(levels(ant.combined$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear combined Models and Follow-ups (Log and Raw RT)

# Combined Model (Log RT)
m.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * c.(Age) +
                   Flanker * c.(Age) +
                   Sex + c.(Education) + c.(Trial),
                 ant.combined)
print(summary(m.combined), cor=F)
cbind(summary(m.combined)$coefficients, p.lmer(m.combined), confint(m.combined, parm="beta_"))

# Combined Model (Raw RT)
m.combined.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                   Cue * Flanker +
                   Cue * c.(Age) +
                   Flanker * c.(Age) +
                   Sex + c.(Education) + c.(Trial),
                 ant.combined)
print(summary(m.combined.raw), cor=F)
cbind(summary(m.combined.raw)$coefficients, p.lmer(m.combined.raw), confint(m.combined.raw, parm="beta_"))
```

```{r}
#| label: Senitivity Analysis for the Combined Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.combined$Participant.RT.log <- ave(log(ant.combined$RT), list(ant.combined$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.combined)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.combined)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.combined[!is.na(ant.combined$Visual_Acuity), ])
length(unique(ant.combined[!is.na(ant.combined$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.combined[!is.na(ant.combined$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.combined[ant.combined$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined[ant.combined$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.combined[ant.combined$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined[ant.combined$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50.combined <- droplevels(ant[ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50.combined$Cue <- factor(ant.acc50.combined$Cue, levels = c("CENTRAL", "DOUBLE", "NOCUE", "SPATIAL"))
levels(ant.acc50.combined$Cue)[levels(ant.acc50.combined$Cue)=="DOUBLE"] <- "CENTRAL"
ant.acc50.combined$Sex <- factor(ant.acc50.combined$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50.combined$Sex) <- matrix(dimnames=list(levels(ant.acc50.combined$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50.combined$Flanker <- factor(ant.acc50.combined$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50.combined$Flanker) <- matrix(dimnames=list(levels(ant.acc50.combined$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50.combined$Cue <- factor(ant.acc50.combined$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50.combined$Cue) <- matrix(dimnames=list(levels(ant.acc50.combined$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50.combined)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.combined[ant.combined$AccuracyAtLeast90==1,])
length(unique(ant.combined[ant.combined$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.combined[ant.combined$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.combined[ant.combined$Age<90,])
length(unique(ant.combined[ant.combined$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.combined[ant.combined$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))
```

## Double Model (Log and Raw RT)

The section has the code for the reproduction of the double models i.e. calculation of alerting and orienting network is done with double cues rather than central cues.

```{r}
#| label: Subset data for Linear Double Model

# Subset (excluded: participants less than 75% accuracy, incorrect responses, double cue trials)
nrow(ant.double <- droplevels(ant[ant$AccuracyAtLeast75==1 & ant$Cue!="CENTRAL" & ant$Accuracy==1,]))
length(unique(ant.double$Participant_ID))
# Contrasts (for Sex, Flanker, and Cue)
ant.double$Sex <- factor(ant.double$Sex, levels=c("Female", "Male"))
(contrasts(ant.double$Sex) <- matrix(dimnames=list(levels(ant.double$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.double$Flanker <- factor(ant.double$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.double$Flanker) <- matrix(dimnames=list(levels(ant.double$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.double$Cue <- factor(ant.double$Cue, levels=c("DOUBLE", "NOCUE", "SPATIAL"))
(contrasts(ant.double$Cue) <- matrix(dimnames=list(levels(ant.double$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))
```

```{r}
#| label: Linear Double Models and Follow-ups (Log and Raw RT)

# Double Model (Log RT)
m.double <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                     Cue * Flanker +
                     Cue * c.(Age) +
                     Flanker * c.(Age) +
                     Sex + c.(Education) + c.(Trial),
                   ant.double)
print(summary(m.double), cor = FALSE)
cbind(summary(m.double)$coefficients, p.lmer(m.double), confint(m.double, parm = "beta_"))

# Double Model (Raw RT) 
m.double.raw <- lmer(RT ~ (1 + Flanker | Participant_ID) +
                     Cue * Flanker +
                     Cue * c.(Age) +
                     Flanker * c.(Age) +
                     Sex + c.(Education) + c.(Trial),
                   ant.double)
print(summary(m.double.raw), cor = FALSE)
cbind(summary(m.double.raw)$coefficients, p.lmer(m.double.raw), confint(m.double.raw, parm = "beta_"))

```

```{r}
#| label: Senitivity Analysis for the Double Linear Model

# Participant Mean log-RT as a Covariate (Random Intercept for this is 0)
ant.double$Participant.RT.log <- ave(log(ant.double$RT), list(ant.double$Participant_ID), FUN = mean)

m.rt <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c.(Trial) + c.(Participant.RT.log),
               ant.double)
print(summary(m.rt), cor = F)
cbind(summary(m.rt)$coefficients, p.lmer(m.rt)) 
confint(m.rt, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# No Covariates
m.nc <- lmer(log(RT) ~ (1 | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age),
               ant.double)
print(summary(m.nc), cor = F)
cbind(summary(m.nc)$coefficients, p.lmer(m.nc))
confint(m.nc, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Visual Acuity as a Covariate
# n of participants without a valid visual acuity score
nrow(ant.double[!is.na(ant.double$Visual_Acuity), ])
length(unique(ant.double[!is.na(ant.double$Visual_Acuity), ]$Participant_ID))

m.vis <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
               Cue * Flanker +
               Cue * c.(Age) +
               Flanker * c.(Age) +
               Sex + c.(Education) + c. (Trial) + c.(Visual_Acuity),
               ant.double[!is.na(ant.double$Visual_Acuity), ])
print(summary(m.vis), cor = F)
cbind(summary(m.vis)$coefficients, p.lmer(m.vis)) 
confint(m.vis, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1600ms
# Data below 1600ms
nrow(ant.double[ant.double$RT<1600,])

m.1600 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.double[ant.double$RT<1600, ])
print(summary(m.1600), cor = F)
cbind(summary(m.1600)$coefficients, p.lmer(m.1600)) 
confint(m.1600, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Responses Faster than 1500ms
# Data below 1500ms
nrow(ant.double[ant.double$RT<1500,])

m.1500 <- lmer(log(RT) ~ (1 + Flanker | Participant_ID) +
                 Cue * Flanker +
                 Cue * c.(Age) +
                 Flanker * c.(Age) +
                 Sex + c.(Education) + c.(Trial),
               ant.double[ant.double$RT<1500, ])
print(summary(m.1500), cor = F)
cbind(summary(m.1500)$coefficients, p.lmer(m.1500)) 
confint(m.1500, parm = c("Cue.ALERTING:C.(Age)","Cue.ORIENTING:C.(Age)", "Cue.EXECUTIVE:C.(Age)"))

# Lenient Exclusion (50% accuracy)
# Subset
nrow(ant.acc50.double <- droplevels(ant[ant$Cue!="CENTRAL" & ant$Accuracy==1,]))
length(unique(ant.acc50$Participant_ID))
ant.acc50.double$Sex <- factor(ant.acc50.double$Sex, levels=c("Female", "Male"))
(contrasts(ant.acc50.double$Sex) <- matrix(dimnames=list(levels(ant.acc50.double$Sex), c(".ME")), c(-0.5, 0.5), nrow=2))
ant.acc50.double$Flanker <- factor(ant.acc50.double$Flanker, levels=c("CONGRUENT", "INCONGRUENT"))
(contrasts(ant.acc50.double$Flanker) <- matrix(dimnames=list(levels(ant.acc50.double$Flanker), c(".EXECUTIVE")), c(-0.5, 0.5), nrow=2))
ant.acc50.double$Cue <- factor(ant.acc50.double$Cue, levels=c("CENTRAL", "NOCUE", "SPATIAL"))
(contrasts(ant.acc50.double$Cue) <- matrix(dimnames=list(levels(ant.acc50.double$Cue), c(".ALERTING", ".ORIENTING")), c(-1/3, 2/3, -1/3, 1/3, 1/3, -2/3), nrow=3))

m.acc50 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.acc50.double)
print(summary(m.acc50), cor=F)
cbind(summary(m.acc50)$coefficients, p.lmer(m.acc50)) 
confint(m.acc50, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Stringent Exclusion (90$ accuracy)
# Data with at least 90%
nrow(ant.double[ant.double$AccuracyAtLeast90==1,])
length(unique(ant.double[ant.double$AccuracyAtLeast90==1,]$Participant_ID))

m.acc90 <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * c.(Age) +
                  Flanker * c.(Age) +
                  Sex + c.(Education) + c.(Trial),
                ant.double[ant.double$AccuracyAtLeast90==1,])
print(summary(m.acc90), cor=F)
cbind(summary(m.acc90)$coefficients, p.lmer(m.acc90)) 
confint(m.acc90, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

# Exclusion of extremely old (<90 only)
# Data with <90
nrow(ant.double[ant.double$Age<90,])
length(unique(ant.double[ant.double$Age<90,]$Participant_ID))

m.neo <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                Cue * Flanker +
                Cue * c.(Age) +
                Flanker * c.(Age) +
                Sex + c.(Education) + c.(Trial),
              ant.double[ant.double$Age<90,])
print(summary(m.neo), cor=F)
cbind(summary(m.neo)$coefficients, p.lmer(m.neo))
confint(m.neo, parm=c("Cue.ALERTING:c.(Age)", "Cue.ORIENTING:c.(Age)", "Flanker.EXECUTIVE:c.(Age)"))

```

## Quadratic Model

The following code produces the reproduction of the quadratic main model as well as the alternate models with quadratic terms

```{r}
#| label: Quadratic Models

# main model (log RT)
m.quad <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.main)
print(summary(m.quad), cor=F)
cbind(summary(m.quad)$coefficients, p.lmer(m.quad))
confint(m.quad, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# main model (raw RT)
m.quad.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.main)
print(summary(m.quad.raw), cor=F)
cbind(summary(m.quad.raw)$coefficients, p.lmer(m.quad.raw))
confint(m.quad.raw, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# double cue model (log RT)
m.quad.double <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.double)
print(summary(m.quad.double), cor=F)
cbind(summary(m.quad.double)$coefficients, p.lmer(m.quad.double))
confint(m.quad.double, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

# combined model (log RT)
m.quad.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                 Cue * Flanker +
                 Cue * poly(c.(Age), 2) +
                 Flanker * poly(c.(Age), 2) +
                 Sex + c.(Education) + c.(Trial),
               ant.combined.corrected)
print(summary(m.quad.combined), cor=F)
cbind(summary(m.quad.combined)$coefficients, p.lmer(m.quad.combined))
confint(m.quad.combined, parm=c("Cue.ALERTING:poly(c.(Age), 2)2", "Cue.ORIENTING:poly(c.(Age), 2)2", "Flanker.EXECUTIVE:poly(c.(Age), 2)2"))

```

## Bi-Linear Model

The following code is for the reproduction of the Bi-Linear model

```{r}
#| label: Bilinear Model (Log and Raw RT) 

# Main Modle (Log RT)
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.fit <- NULL

for(bp in seq(min(ant.main$Age), max(ant.main$Age), 1)){
  ant.main$adj.Age <- ant.main$Age - bp
  ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)
  m.current <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp) +
                      Flanker * (adj.Age + adj.Age:post.bp) +
                      Sex + c.(Education) + c.(Trial),
                    ant.main, REML=F)
  m.current.fit <- data.frame(Breakpoint=bp, Deviance=deviance(m.current, REML=F), AIC=AIC(m.current))
models.fit <- rbind(models.fit, m.current.fit)}

# Best breakpoint
models.fit[models.fit$AIC==min(models.fit$AIC),]
bp <- models.fit[models.fit$AIC==min(models.fit$AIC),]$Breakpoint

# Make indicator variable
ant.main$adj.Age <- ant.main$Age - bp
ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)

# Model
m.break <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp) +
                  Flanker * (adj.Age + adj.Age:post.bp) +
                  Sex + c.(Education) + c.(Trial),
                ant.main)
print(summary(m.break), cor=F)
cbind(summary(m.break)$coefficients, p.lmer(m.break))
confint(m.break, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.fit$deltaAIC <- models.fit$AIC - min(models.fit$AIC)

ggplot(models.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint (Log RT) Search Using AIC"
    ) +
    theme_classic()

# Main Model (Raw RT)
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.fit.raw <- NULL

for(bp in seq(min(ant.main$Age), max(ant.main$Age), 1)){
  ant.main$adj.Age <- ant.main$Age - bp
  ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)
  m.current.raw <- lmer(RT ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp) +
                      Flanker * (adj.Age + adj.Age:post.bp) +
                      Sex + c.(Education) + c.(Trial),
                    ant.main, REML=F)
  m.current.fit.raw <- data.frame(Breakpoint=bp, Deviance=deviance(m.current.raw, REML=F), AIC=AIC(m.current.raw))
models.fit.raw <- rbind(models.fit.raw, m.current.fit.raw)}

# Best breakpoint
models.fit.raw[models.fit.raw$AIC==min(models.fit.raw$AIC),]
bp.raw <- models.fit.raw[models.fit.raw$AIC==min(models.fit.raw$AIC),]$Breakpoint

# Make indicator variable
ant.main$adj.Age <- ant.main$Age - bp
ant.main$post.bp <- as.numeric(ant.main$adj.Age>0)

# Model
m.break.raw <- lmer(RT ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp) +
                  Flanker * (adj.Age + adj.Age:post.bp) +
                  Sex + c.(Education) + c.(Trial),
                ant.main)
print(summary(m.break.raw), cor=F)
cbind(summary(m.break.raw)$coefficients, p.lmer(m.break.raw))
confint(m.break.raw, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.fit.raw$deltaAIC <- models.fit.raw$AIC - min(models.fit.raw$AIC)

ggplot(models.fit.raw, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint (Raw RT) Search Using AIC"
    ) +
    theme_classic()

# Double Model
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.double.fit <- NULL

for(bp.d in seq(min(ant.double$Age), max(ant.double$Age), 1)){
  ant.double$adj.Age <- ant.double$Age - bp.d
  ant.double$post.bp.d <- as.numeric(ant.double$adj.Age>0)
  m.current.double <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp.d) +
                      Flanker * (adj.Age + adj.Age:post.bp.d) +
                      Sex + c.(Education) + c.(Trial),
                    ant.double, REML=F)
  m.current.double.fit <- data.frame(Breakpoint=bp.d, Deviance=deviance(m.current.double, REML=F), AIC=AIC(m.current.double))
models.double.fit <- rbind(models.double.fit, m.current.double.fit)}

# Best breakpoint
models.double.fit[models.double.fit$AIC==min(models.double.fit$AIC),]
bp.d <- models.double.fit[models.double.fit$AIC==min(models.double.fit$AIC),]$Breakpoint

# Make indicator variable
ant.double$adj.Age <- ant.double$Age - bp.d
ant.double$post.bp.d <- as.numeric(ant.double$adj.Age>0)

# Model
m.break.double <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp.d) +
                  Flanker * (adj.Age + adj.Age:post.bp.d) +
                  Sex + c.(Education) + c.(Trial),
                ant.double)
print(summary(m.break.double), cor=F)
cbind(summary(m.break.double)$coefficients, p.lmer(m.break.double))
confint(m.break.double, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.double.fit$deltaAIC <- models.double.fit$AIC - min(models.double.fit$AIC)

ggplot(models.double.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp.d, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint Double (Log RT) Search Using AIC"
    ) +
    theme_classic()

# Combined Model
# (no random slope due to non-convergence; REML=F more appropriate for model comparisons)
models.combined.fit <- NULL

for(bp.c in seq(min(ant.combined$Age), max(ant.combined$Age), 1)){
  ant.combined$adj.Age <- ant.combined$Age - bp.c
  ant.combined$post.bp.c <- as.numeric(ant.combined$adj.Age>0)
  m.current.combined <- lmer(log(RT) ~ (1|Participant_ID) +
                      Cue * Flanker +
                      Cue * (adj.Age + adj.Age:post.bp.c) +
                      Flanker * (adj.Age + adj.Age:post.bp.c) +
                      Sex + c.(Education) + c.(Trial),
                    ant.combined, REML=F)
  m.current.combined.fit <- data.frame(Breakpoint=bp.c, Deviance=deviance(m.current.combined, REML=F), AIC=AIC(m.current.combined))
models.combined.fit <- rbind(models.combined.fit, m.current.combined.fit)}

# Best breakpoint
models.combined.fit[models.combined.fit$AIC==min(models.combined.fit$AIC),]
bp.c <- models.combined.fit[models.combined.fit$AIC==min(models.combined.fit$AIC),]$Breakpoint

# Make indicator variable
ant.combined$adj.Age <- ant.combined$Age - bp.c
ant.combined$post.bp.c <- as.numeric(ant.combined$adj.Age>0)

# Model
m.break.combined <- lmer(log(RT) ~ (1+Flanker|Participant_ID) +
                  Cue * Flanker +
                  Cue * (adj.Age + adj.Age:post.bp.c) +
                  Flanker * (adj.Age + adj.Age:post.bp.c) +
                  Sex + c.(Education) + c.(Trial),
                ant.combined)
print(summary(m.break.combined), cor=F)
cbind(summary(m.break.combined)$coefficients, p.lmer(m.break.combined))
confint(m.break.combined, parm=c("Cue.ALERTING:adj.Age:post.bp", "Cue.ORIENTING:adj.Age:post.bp", "Flanker.EXECUTIVE:adj.Age:post.bp",
                        "Flanker.EXECUTIVE:adj.Age"))

# Figure showing Breakpoint Search
models.combined.fit$deltaAIC <- models.combined.fit$AIC - min(models.combined.fit$AIC)

ggplot(models.combined.fit, aes(x = Breakpoint, y = deltaAIC)) +
    geom_line(linewidth = 1) +
    geom_point(size = 2) +
    geom_vline(xintercept = bp.c, linetype = "dotted", linewidth = 0.8) +
    labs(
        x = "Age Breakpoint",
        y = expression(Delta*AIC),
        title = "Breakpoint combined (Log RT) Search Using AIC"
    ) +
    theme_classic()
```

# Reliability

For the purposes of reliability we have chosen Spearman Brown Intraclass Correlation Coefficient (S-B) and Guttman. Which are the two most popular reliability measures in ANT literature. Both are split-half and S-B is run with 10000 permutations as in literature prior.

```{r}
#| label: Multi Permutation Correlation Reliability ICC
set.seed(1996)

n_perm <- 10000
exec_corrs <- numeric(n_perm)
alert_corrs <- numeric(n_perm)
orient_corrs <- numeric(n_perm)
alert_d_corrs <- numeric(n_perm)

# Alerting
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Alerting network score
  alert_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Alert_Net = RT[Cue == "NOCUE"] -
                 RT[Cue == "CENTRAL"],
      .groups = "drop"
    )

  alert_gutt_random <- alert_score_random |>
    pivot_wider(names_from = split, values_from = Alert_Net)

  # Split-half correlation
  alert_corrs[i] <- icc(alert_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}

alert_corrs_SB <- (2 * alert_corrs) / (1 + alert_corrs)
alert_est <- median(alert_corrs_SB, na.rm = TRUE)
alert_CI <- quantile(alert_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(alert_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Executive
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Flanker) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Executive network score
  exec_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Flanker) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Exec_Net = RT[Flanker == "INCONGRUENT"] -
                 RT[Flanker == "CONGRUENT"],
      .groups = "drop"
    )

  exec_gutt_random <- exec_score_random |>
    pivot_wider(names_from = split, values_from = Exec_Net)

  # Split-half correlation
  exec_corrs[i] <- icc(exec_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
exec_corrs_SB <- (2 * exec_corrs) / (1 + exec_corrs)
exec_est <- median(exec_corrs_SB, na.rm = TRUE)
exec_CI <- quantile(exec_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(exec_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Orienting
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Orienting network score
  orient_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Orient_Net = RT[Cue == "CENTRAL"] -
                 RT[Cue == "SPATIAL"],
      .groups = "drop"
    )

  orient_gutt_random <- orient_score_random |>
    pivot_wider(names_from = split, values_from = Orient_Net)

  # Split-half correlation
  orient_corrs[i] <- icc(orient_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
orient_corrs_SB <- (2 * orient_corrs) / (1 + orient_corrs)
orient_est <- median(orient_corrs_SB, na.rm = TRUE)
orient_CI <- quantile(orient_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)
hist(orient_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")

# Alerting Double
for (i in seq_len(n_perm)) {

  ant_gutt_random <- droplevels(
    ant[ant$AccuracyAtLeast75 == 1 & ant$Accuracy == 1, ]
  ) |>
    group_by(Participant_ID, Cue) |>
    mutate(split = sample(rep(c("A", "B"), length.out = n()))) |>
    ungroup()

  # Alerting network score
  alert_d_score_random <- ant_gutt_random |>
    group_by(Participant_ID, split, Cue) |>
    summarise(RT = mean(RT, na.rm = TRUE), .groups = "drop") |>
    group_by(Participant_ID, split) |>
    summarise(
      Alert_Net = RT[Cue == "NOCUE"] -
                 RT[Cue == "DOUBLE"],
      .groups = "drop"
    )

  alert_d_gutt_random <- alert_d_score_random |>
    pivot_wider(names_from = split, values_from = Alert_Net)

  # Split-half correlation
  alert_d_corrs[i] <- icc(alert_d_gutt_random[, c("A", "B")],
                        model = "twoway",
                        type = "consistency",
                        unit = "single")$value
}
alert_d_corrs_SB <- (2 * alert_d_corrs) / (1 + alert_d_corrs)
alert_d_est <- median(alert_d_corrs_SB, na.rm = TRUE)
alert_d_CI <- quantile(alert_d_corrs_SB,
                    c(0.025, 0.975),
                    na.rm = TRUE)

hist(alert_d_corrs,
     breaks = 50,
     main = "Permutation-based split-half correlations",
     xlab = "Correlation")
```
